\documentclass[
  english,
  font=times,
  twocolumn,
]{tumarticle}

\usepackage{cite}
\usepackage{booktabs}
\usepackage{float}
\usepackage{placeins}

\title{Group Assignment -- Business Process Prediction, Simulation, and Optimization}
\subtitle{A Data-Driven Simulation Model and Resource-Allocation Optimization on the BPIC-17 Event Log}

\author[email=aldo.patrone@tum.de]{Aldo Patrone}
\author[email=go34bef@tum.de]{Can Güleç}
\author[email=member3@tum.de]{Group Member 3}
\author[email=member4@tum.de]{Group Member 4}

\date\today

\begin{document}

\maketitle

\begin{abstract}
We build a data-driven business process simulation of the BPI Challenge 2017 loan
application process and optimize its resource allocation. In Part~I, a discrete-event
simulation engine enacts a discovered process model and routes cases through it,
with data-fitted case arrivals, processing times, branching decisions and resource
availabilities, permissions and allocation. In Part~II, the random baseline
allocation is replaced by heuristic and learning-based policies and evaluated on
cycle time, resource occupation and fairness. We report our design decisions,
empirical results and the applicability of each approach.
\end{abstract}

\section{Introduction}
Business process simulation enables what-if analysis and optimization of process
performance without intervening in the real system. In this group project we build
a \emph{data-driven} simulation of the BPI Challenge 2017 (BPIC-17) loan application
process and use it to study resource-allocation policies.

\emph{Part~I} develops the simulation model: a discrete-event engine with a single
global event queue (Sec.~\ref{sec:sim}) that simulates case arrivals, enforces a
discovered process model, samples processing and waiting times, makes branching
decisions and constrains execution by resource availabilities, permissions and
allocation. \emph{Part~II} (Sec.~\ref{sec:opt}) optimizes the resource allocation
procedure, comparing heuristic and reinforcement-learning policies under several
metrics. All components are fit on the real BPIC-17 event log. Section~\ref{sec:ai}
documents our use of AI tools.

\section{Simulation Model (Part~I)}\label{sec:sim}

\subsection{Simulation Engine Core}
\textit{(Thomas P. Hartel, 1.1)}\quad

For the discrete simulation core, a priority queue is used with a custom priority rule based on the simulation time point, the event type and otherwise on the case ID. The latter ensures that there is always a clear order. The event type ensures that activities are terminated first before others are resumed and before any new activity is started. This is only logical because it ensures that resources are freed as soon as possible and can take up a new activity as soon as they finish their last one.
Each event and case is modelled as its own class and equipped with attributes that can be jointly retrieved and updated in the standard XES format.

For case arrival, attributes are sampled according to conditional probabilities when sufficient data is available. Otherwise, fallbacks are used. For each case, the last $n$ ($n \in \mathbb N$) or all events can be returned, as well as a count of how often an activity occurs in a case up to that moment. This is important in feature construction for machine learning. The log can be exported to xes, csv or both which is implemented via an own class.

Note that the case arrival is modelled seperatly from the start of the first activity because the latter requires a resource to be assigned. This choice keeps th model more flexible. If no resource can be assigned to an event, the event is not logged. This is in line with the sample log.

The engine core provides a method to suspend activities so that this can be simulated by resource allocation approaches.

\subsection{Case Arrivals} \textit{(Can Güleç, 1.2)}
The case arrival engine handles when new process instances show up during the simulation. Instead of just sampling arrival times from one static distribution (the simple approach), we use dynamic arrival rates that change depending on the time of day and day of the week. 

During training, the engine analyzes the event log to determine a base arrival frequency. It gets the first timestamp of every unique process instance, sorts them chronologically, and calculates the time gaps between case starts that come after each other. The base rate, which we feed into an exponential distribution, $X_0 \in \mathbb{R}^+$ is simply the average of these inter-arrival gaps:
$$X_0 = \frac{1}{N-1} \sum_{i=2}^{N} (t_i - t_{i-1})$$
where $t_i$ is the start timestamp of case $i$, and $N$ is the total number of cases. Training on the BPIC-17 log gives us a baseline of $X_0 \approx 1002.23\,\text{s}$.

Then, during simulation, this baseline rate gets adjusted using multipliers tied to the current weekday and hour. Let $w(t) \in \{0, \dots, 6\}$ represent the day of the week and $h(t) \in \{0, \dots, 23\}$ the hour for a given simulation timestamp $t$. The resulting dynamic scale parameter $S(t)$ is:
$$S(t) = \frac{X_0}{M_{\text{day}}(w(t)) \cdot M_{\text{hour}}(h(t))}$$

As shown in Figure \ref{fig:availability}, the modifiers peak during standard weekday business hours, leading to faster case arrivals (shorter gaps between instances). In the evenings and on weekends, the modifiers drop, slowing arrivals down (longer gaps between instances). The actual waiting time $\Delta t$ until the next case arrives is then sampled from an exponential distribution using this adjusted rate:
$$\Delta t \sim \text{Exponential}\left(\lambda = \frac{1}{S(t)}\right)$$

This design was inspired by Kirchdorfer et al. (2025) \cite{kirchdorfer2025divide}, who make a strong case for preserving intraday and weekday dynamics in order to avoid distorting business process simulations. We didn't go as far as their full AT-KDE method, which uses clustering and kernel density estimation to automatically learn arrival patterns from historical data. Instead, we went with a simpler, more hands-on approach, manually defining multipliers that still capture the key weekday and time of the day effects.

\subsection{Processing Times}
\textit{(Thomas P. Hartel, 1.3)}\quad

The process time engine provides the processing and waiting times for the engine.
For all models, processing and waiting times are computed seperatly.

For the standard basic modells, a binomial model tracks the proportion of zero-duration events to accurately sample instantenous tasks. Then, a Gamma, a Lognormal and a Poisson distribution are fitted to the non-zero timespans for each combination of activity and resource. The optimal distribution is automatically selected by the Akaike Information Criterion based on the number of parameters and the likelihood. If there is insufficient data to fit the combination of activity and resource, the three distributions are fitted only to the activity.

For the advanced contextual model a Random Forest Regressor is employed. The pipeline uses a Column Transformer to handle missing values via median imputation and categorical variables via one-hot encoding. This allows the model to predict times based on the specific attributes of a case at a given moment. Additionally, the hour of day and the weekday at event start are used as variables. Also a variable counting how often this activity occured in the case, is used. This can be reasonable as it a repeated activity may be faster than the first one.

For uncertainty estimation, a quantile regression based on a Gradient Boosting Tree is used. By training pipelines for the $25$th, $50$th, and $75$th percentiles, the engine does not just output a static expected value. Instead, it provides a probabilistic bounds estimation, which is vital for risk assessment in process execution.

To prevent retraining the model for every simulation run, the models are stored. If they are found at the respective path, the models are just loaded instead of retrained.


\subsection{Process Model}
\textit{(Can Güleç, 1.4)}\quad
The process model engine (BPMNEngine in code) enforces the control flow of each simulated process instance. The engine we implemented will load a BPMN file using PM4Py and convert this file to a Petri net. This way, our engine supports the use of any type of process model. In our example, the process model is loaded from \texttt{models/v4\_replay.bpmn}, which represents the BPI Challenge 2017 loan application process The final Petri net, with its initial and final markings, represents the executable form of the process model. Each simulated case has its own Petri net marking. Thus, multiple process instances can progress independently. 

\subsubsection{Tracking Tokens and Firing Transitions}
During simulation, the engine uses the Petri net semantics provided by PM4Py to discover enabled transitions. Each case's progress through the process is tracked independently. The engine keeps a simple dictionary mapping each \textbf{case\_id} to its own current marking. When the scheduler asks the engine what a case can do next (via \textbf{getPossibleNextActivities}), the engine checks the standard Petri net firing rule against that case's current marking: a transition $t \in T$ is enabled only if every one of its input places has at least one token:
$$\forall p \in \bullet t: M(p) \geq 1$$
If a transition is enabled, the engine can fire it by moving tokens out of the input places and into the output places to produce the new marking:
$$M' = (M - \bullet t) + t\bullet$$

\subsubsection{Handling Silent Transitions with BFS}
 Invisible transitions can be created during the BPMN to Petri net conversion because real-world process models (like BPIC-17) are full of routing logic. The parallel splits, XOR gateways, loops, etc. show up as unlabeled transitions in the Petri net. If the engine only looked at visible activities, it would get stuck behind these silent gateways and think the process had deadlocked, even though it hadn't. To overcome this problem, we added a breadth first search step inside the state-checking logic. The transitions are automatically traversed with it until a visible activity is found. Therefore, the engine can identify all possible executable activities. Once an activity is executed, the transition corresponding to the activity is fired and the case marking is updated. Since the engine updates the case marking after every activity is executed, every simulated case is guaranteed to follow the control flow defined by the BPMN model.

\subsection{Branching Decisions}
\textit{(Joao, 1.5)}\quad
\input{sections/branching_joao}

\subsubsection{Evaluation}
\textit{(Joao)}\quad
\input{sections/branching_eval_joao}

\input{sections/resource_modeling}

\section{Optimization (Part~II)}\label{sec:opt}

\input{sections/heuristics}
\input{sections/batch_allocation}

\subsection{Advanced Formalization}\label{subsec:formalization}
\input{sections/formalization_kunkler}
\input{sections/formalization_park}

\input{sections/rl_allocation}

\subsection{Evaluation Metrics}\label{subsec:eval-metrics}
\input{sections/metrics_simple}
\input{sections/metrics_custom}

\subsection{Evaluation}\label{subsec:eval}

\subsubsection{Settings and Protocol}
\textit{(Joao, F)}\quad
\input{sections/evaluation_protocol_joao}

\subsubsection{Base Heuristics}
\textit{(Joao, A)}\quad
\input{sections/base_heuristics_eval_joao}

\subsubsection{Kunkler Formalization}
\textit{(Thomas, C)}\quad

\subsubsection{Park Formalization}
\textit{(Joao, C)}\quad
\input{sections/parksong_eval_joao}

\input{sections/rl_evaluation}

\subsubsection{Cross-Method Synthesis}\label{ssub:cross-eval}
\textit{(Joao, F)}\quad
\input{sections/cross_method_joao}

\subsubsection{Slide-23 Question}
\textit{(Can Güleç, Slide 23 Scenario Analysis)}\quad

\paragraph{Resource Selection}
The question we selected to answer is the first one on slide 23. The management wants us to fire two employees. To address this request, we ranked all 149 resources by their occupation (busy time divided by available time), using the resource availability calendars learned in Task 1.6. Before selecting the least utilized resources, we excluded two categories:
\begin{itemize}
    \item {User\_1} was excluded because it is not a valid employee. Although its occupation is nearly zero, it generated over 148000 log events consisting almost entirely of automatic system activities and queue offers.
    \item {Near-empty resources} Users \_147, \_148 and \_149 were also not counted since they appear only 1-4 times in the log, making their removal meaningless as they are already barely present in the data.
\end{itemize}

From the remaining active employees, we selected the two resources with the lowest occupation. It was verified that their removal would not leave any activity without sufficient qualified resources, using the authorization data from Task 1.7.
The resources we selected to remove are
\begin{itemize}
    \item \textbf{User\_76:} 2.3\% occupation, 1{,}028 logged events, authorized for
    23 of 26 activities.
    \item \textbf{User\_108:} 2.4\% occupation, 753 logged events, authorized for
    23 of 26 activities.
\end{itemize}
\paragraph{Impact on Metrics}
To evaluate the effect of removing the selected resources, the simulation was rerun after excluding User\_76 and User\_108 from the resource pool. The following table summarizes the results: ,
\begin{table}[H]
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{lccc}
\toprule
Scenario & Cycle time (days) & Occupation & Fairness (Gini) \\
\midrule
Baseline (149 resources) & 0.25 & 0.164 & 0.801 \\
After removal (147 resources) & 0.26 & 0.159 & 0.808 \\
\bottomrule
\end{tabular}
}
\caption{Simulated impact of removing User\_76 and User\_108}
\end{table}
As expected, removing two resources caused only a very small increase in average cycle time (0.25 to 0.26 days), indicating that the overall processing capacity is largely unaffected. This is consistent with the low utility of the selected resources. The remaining metrics changed only slightly. The average resource occupation decreased slightly, despite the reduced workforce, because the simulation also completed slightly fewer cases (579 instead of 583). Similarly, the fairness metric (Gini) increased only by 0.007. This suggests a slightly less balanced workload distribution after the remaining tasks were redistributed among the available resources.
Overall, the experiment confirms that removing User\_76 and User\_108 has a very minor impact on system performance. The observed differences are small and likely influenced by the stochastic nature of the simulation. A better assessment would repeat both scenarios with multiple random seeds and compare the results.

\section{Use of AI Tools}\label{sec:ai}
\input{sections/ai_tools}

\bibliographystyle{plain}
\bibliography{references}

\appendix
\input{sections/appendix}
\input{sections/joao_appendix}

\end{document}
