The fixed-replay comparison includes the five methods evaluated under the same
integrated protocol. The reinforcement-learning policy is reported separately
because it was tested in a different environment and is therefore not directly
comparable to these results.

\begin{table}[H]
    \caption{Canonical fixed-replay allocation comparison over five seeds.}
    \label{tab:cross_method_fixed_replay_joao}
    \centering
    \renewcommand{\arraystretch}{1.0}
    \scriptsize
    \resizebox{\columnwidth}{!}{
    \begin{tabular}{lrrrrr}
        \toprule
        \textbf{Method}
        & \textbf{Completion}
        & \textbf{Cycle h}
        & \textbf{Wait min}
        & \textbf{Gini}
        & \textbf{Weighted fair.} \\
        \midrule
        R-RRA
        & $1.0000$ & $29.2187$ & $27.2885$ & $0.5327$ & $0.0053$ \\
        R-SHQ
        & $0.9974$ & $18.1068$ & $27.9555$ & $0.4738$ & $0.0032$ \\
        ParkSong-Composite
        & $1.0000$ & $32.2304$ & $73.3656$ & $0.5284$ & $0.0044$ \\
        Kunkler-Rinderle-Ma
        & $0.9974$ & $28.7661$ & $27.2548$ & $0.4896$ & $0.0054$ \\
        Batch
        & $0.9974$ & $19.9040$ & $27.3101$ & $0.4912$ & $0.0054$ \\
        \bottomrule
    \end{tabular}
    }
\end{table}

No method dominates every metric. R-SHQ has the lowest conditional mean cycle
time and the lowest Gini and weighted fairness values, but leaves one fixed
route incomplete. R-RRA and ParkSong-Composite complete all fixed-route runs,
while Kunkler-Rinderle-Ma has the lowest mean waiting time by a small margin
over R-RRA and Batch.

ParkSong-Composite demonstrates that prediction-aware reservations can be
integrated into the simulator, but its performance depends on prediction
quality, processing-time coverage, and the operational cost of keeping
resources idle. Its results confirm that the reservation mechanism is
functional, not that it outperforms reactive allocation under every workload.

Cycle time is conditional on completion and must therefore be interpreted
jointly with the completion rate. The results are descriptive over $76$
historical routes and five seeded repetitions and are not presented as
universal performance guarantees. Per-seed results and ParkSong diagnostics
are reported in App.~\ref{app:joao-fixed-replay-details} and
App.~\ref{app:joao-parksong-diagnostics}.