\subsection{Base Allocation Heuristics}
\label{subsec:heuristics}
\textit{(João, A)}\quad

We adapted the round-robin and shortest-queue workflow resource patterns to the simulator's uncertain availability and permission constraints \cite{russell2005workflow}. Both methods use the
same filtered simulator state. A resource is considered only if it is currently
available, idle, and authorized for the task. Tasks must be enabled,
unassigned, unblocked, and compatible with the resource permissions.

The methods account for uncertain availability by checking the available
resources again at every allocation decision. They do not predict future
resource calendars~\cite{pufahl2025resourceallocation}.

\noindent\textbf{Resource-aware Round Robin (R-RRA).}
R-RRA cycles through eligible resources in a deterministic order based on the
resource identifier. A persistent pointer is kept between allocation calls.
Each resource receives its oldest eligible waiting task, with the task
identifier used to resolve ties. The pointer is updated only after an
assignment.

\noindent\textbf{Resource-aware Shortest Queue (R-SHQ; cumulative-load adaptation).} R-SHQ balances cumulative assignments rather than an instantaneous per-resource queue length. It
uses \texttt{ResourceEngine.load}, which increases whenever a resource receives
a task and is not reduced when the resource becomes available again.

Tasks are ordered by enabled time, decreasing priority, and task identifier.
For each task, the method selects the available and authorized resource with the
lowest cumulative load. Ties are resolved by resource identifier, and missing
load values are treated as zero.

R-SHQ is a myopic heuristic: it uses the current simulator state and previous
assignments, but does not consider future arrivals, calendars, processing
times, or remaining workloads. Detailed results for seeds $1$--$5$ are reported
in App.~\ref{app:joao-fixed-replay-details}.