\subsubsection{Custom Metric}\label{ssub:metrics-custom}
\textit{(Thomas, G)}\quad

The custom metrics are designed to evaluate the operational friction and workforce specialization of the resource allocation strategy. They aim to combine aspects from information theory, graph theory and flow theory to offer an advanced summary on a broad theoretical basis.

To evaluate handoff dynamics, the following two metrics were employed:
The \emph{average handovers per case} measures the number of a case's transitions between resources. While some handovers are necessary, excessive handovers can lead to unnecessary communication.
The \emph{Average Rework Rate} measures how often an activity is executed within the same case. This can indicate quality or data issues, e.g., regularly missing information from customers.

Additionally, we wanted to create metrics to detect structural process vulnerabilities. 
The \emph{activity entropy per resource} measures how evenly an activity is distributed across resources. A high entropy indicates that the work is shared relatively evenly among multiple resources, and lower entropy indicates that one or a few resources perform most or all instances of the activity. This metric is highly relevant because it provides insight into the distribution of organizational knowledge and skills. High entropy suggests that knowledge is widely distributed, making the processes resilient. If an activity has low entropy, it can indicate a critical dependence on individual employees, increasing the risk of process disruptions, e.g., due to absence. Additionally, this reflects the resource's value to the process: the procedural value of each activity is calculated as 1 minus the normalized entropy. By summing all values per resource, we obtain a metric that describes the value each resource provides to the process. Intuitively, this can be described as the salary a person may demand solely based on their relevance to the value chain.\footnote{In practice, salaries are shaped by numerous non‑procedural factors, including tenure at the company.} By adding those up, we get an idea of the \emph{total procedural resource costs}.

For the next metric, the idea of structural process vulnerabilities is picked up and taken to a systematic level: To evaluate the robustness of the collaboration network, the resource handoffs are treated as a graph. Based on that, a symmetrisised adjacency graph is calculated where each entry describes the number of hand-offs between the resources. Even though it is more intuitive to choose a directed graph, the theory of eigenvalues does not apply well in this case. Similar to singular value decomposition, a lot of the theoretical foundations fall apart when using non-symmetric matrices. \footnote{Note, however, that the right eigenvalues group nodes based on their downstream influence, whereas the left eigenvector groups nodes based on their upstream influence. As we want both effects, the symmetrization is reasonable.}
Based on that, the \emph{algebraic connectivity} is calculated. It measures how well-connected the organizational network is and how easily it can be fragmented into isolated sub-components. A higher $\lambda_2$ value indicates a highly cohesive, collaborative environment in which resources frequently interact. A value near zero indicates structural vulnerabilities, such as siloed departments. This idea is based on (Fiedler, 1973).

Taking the bottleneck analysis one step further, the final metrics try to analyse congestions. One metric measures how strongly one event's suspension effects other events that run in the close future (one day time window). By counting how many suspensions follow within one day after a suspension, we get a metric quantifying the jamming of events, called \emph{supsension contagion}. Intuitively this quantifies how a tense resource allocatoin spreads if the system is close to its maximal load. (If there are many efficient resources to choose from no event has to be suspended.) As such, it is very important for operational resilience.
The other metric is based on the fact that an event-start is logged only if a resource is assigned to that event. As such, the waiting time includes any delays that are due to overloads. It is assumed that, if a waiting time is more than two times as long as the mean waiting time, this is due to unavailable delay due to resource assignment. With that, comparative straint values can be calculated. Notice, that if our Simulation Engine is used directly, we could just safe and store the correct time. Even though I implemented this, comparing logs would be difficult. After exponentially weighting the events within the next $24$-hours, the effect of an activity's strain on the future can be measured.


\begin{table}[!h]
    \caption{Evaluation metrics on the real BPIC-17 log.}
    \centering
    \begin{tabular}{lr}
        \textbf{Metric} & \textbf{Value} \\
        Average Handovers per Case      & $6.91$ days \\
        Average Rework Rate             & $0.04$ \\
        Total processoral value         & $25680.40$ \\
        Network Algebraic Connectivity  & $1.9976$ \\
        Efect of Suspensions            & $691.24$ \\
    \end{tabular}
\end{table}