\subsubsection{Reinforcement-Learning Policy}\label{ssub:rl-eval}
\textit{(Aldo Patrone)}\quad
\textbf{Setup.} Both learned policies (Sec.~\ref{subsec:rl}), the paper-faithful MaskablePPO and the
lightweight numpy REINFORCE, are evaluated in the same discrete-event environment they are trained
in, the setting Middelhuis et al.\ also evaluate in, against four baselines that make the same
$(\text{resource},\text{activity})$ decisions: random, round-robin, shortest-queue and
most-experienced. All are scored on the paper's objective (mean cycle time) and on load fairness over
$25$ evaluation episodes at $w_{\mathrm{fair}}=1$ (Table~\ref{tab:alloc_sim}). The reward carries a
small postpone cost, without which the high-variance REINFORCE degenerates into a wait-only policy
that completes no cases. The MaskablePPO learning curve is in
Fig.~\ref{fig:rl_curve}, and a fairness-weight sensitivity ($w_{\mathrm{fair}}\in\{0,1,5\}$) for both
learned methods is in Fig.~\ref{fig:alloc_cmp_plot}.

\begin{table}[!h]
    \caption{Allocation methods in the paper-faithful environment (state $2|R|+|A|$, $(r,a)$ action
    space, cycle-time reward plus a small postpone cost), mean over $25$ evaluation episodes at
    $w_{\mathrm{fair}}=1$. The heuristic baselines are this environment's own implementations, not the
    Part-II-A strategies of Sec.~\ref{ssub:cross-eval}. Lower Gini is fairer.}
    \centering
    \renewcommand{\arraystretch}{1.2}
    \footnotesize
    \begin{tabular}{lcc}
        \toprule
        \textbf{Method} & \textbf{Cycle time (h)} & \textbf{Load Gini} \\
        \midrule
        Random            & $4.88$ & $0.267$ \\
        Round-robin       & $4.83$ & $0.263$ \\
        Shortest-queue    & $4.75$ & $\mathbf{0.164}$ \\
        Most-experienced  & $4.60$ & $0.397$ \\
        REINFORCE         & $4.76$ & $0.407$ \\
        PPO (MaskablePPO) & $5.14$ & $0.378$ \\
        \bottomrule
    \end{tabular}
    \label{tab:alloc_sim}
\end{table}

\textbf{Result.} The finding is a robust \emph{negative} one: neither learned policy beats the simple
heuristics. Cycle times cluster tightly across all six methods ($4.6$--$5.1$\,h), within the
run-to-run variance discussed below, so the allocation choice barely moves the objective. On fairness
the picture is clearer: shortest-queue is decisively best ($0.164$ Gini) and the load-balancing
baselines random and round-robin sit at $0.26$--$0.27$, whereas both learned policies are among the
\emph{least} fair (REINFORCE $0.407$, PPO $0.378$, comparable to most-experienced's $0.397$) because
they concentrate work on few resources. So the learned policies neither speed the process up nor
distribute it more evenly than a one-line heuristic. The MaskablePPO learning curve confirms it
trains (returns rise and plateau over $750$ episodes), so this is a genuine result and not a broken
run.

\textbf{Interpretation.} The explanation is structural and matches the paper's own observation that
well-matched heuristics are strong: shortest-queue is near-optimal for a load-balancing fairness
objective, and in this process the cycle time is dominated by arrivals and processing times rather
than by which eligible resource is chosen. Figure~\ref{fig:rl_load} makes this visible, shortest-queue
spreads work most evenly while the learned policies concentrate it on few resources. The
fairness-weight sensitivity (Fig.~\ref{fig:alloc_cmp_plot}) shows no clean trend for either learned
method: sweeping $w_{\mathrm{fair}}\in\{0,1,5\}$ moves their Gini only within a noisy $0.35$--$0.42$
band and never toward the shortest-queue level. That noise is expected because the arrival stream is
not reseeded per episode, so absolute cycle times and Gini values carry a run-to-run variance of a few
percent, an honest limitation of this standalone environment. The robust conclusion survives it: for
this process and objective a learned allocation policy is \emph{not} justified over a one-line
heuristic. Deep RL would pay off in settings with sharper resource-activity specialization or binding
capacity constraints, where the assignment actually changes the cycle time.

\textbf{Deployment.} The trained policy also deploys onto the integrated \emph{SimulationEngineCore}
through the \emph{PPOAllocation} strategy (the per-task reduction of Sec.~\ref{subsec:rl}), which we
validated structurally. A full integrated multi-seed rerun of the deep model requires the engine's
XES reader and the original processing-time model together with the sb3 stack in a single
environment. The group-wide comparison of the other allocation methods is reported in
Sec.~\ref{ssub:cross-eval}, but it runs in the integrated fixed-replay engine rather than the
paper-faithful environment used here, so its absolute cycle times and Gini values are on a different
scale and are not directly comparable to Table~\ref{tab:alloc_sim}.
